Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2016-01-31 document/ms.tex
method intro words

To study the occurrence rate of long-period exoplanets, we developed a
fully-automated method for searching the archival \kepler\ light curves for
these systems with only one or two transits.

>>>>

To study the occurrence rate of long-period exoplanets, we have developed a
fully-automated method for searching the archival \kepler\ light curves for
these systems with only one or two transits.
Using this method, we detect XXX long-period transiting planet candidates and
YYY long-period eclipsing binary candidates.
We estimate that the population level false positive rate in this exoplanet
candidate sample is about ZZZ\%.
By injecting synthetic transit signals into the \kepler\ light curves, we
measure the completeness of our search method.
Based on this catalog of exoplanet candidates and the search completeness, we
constrain the occurrence rate of long-period exoplanets.
For large planets, these results are consistent with previous measurements of
long-period, giant planet occurrence rates based on radial velocity surveys
and we demonstrate that small---and possibly rocky---planets are more common
than their larger counterparts even at long orbital periods.

\section{The search for long-period exoplanets}

Data from the \kepler\ Mission has been used to discover a diverse zoo of
thousands of exoplanets of all sizes orbiting stars of all types.
It has be demonstrated that these discoveries can be used to place constraints
on the occurrence rate of exoplanets \dfmtodo{CITE}.
These results are sensitive to the detection efficiency and reliability of the
transit discovery methods \dfmtodo{CITE Burke}.

The search for long-period planets presents several unique challenges.
Of these, the most important is the inevitable sensitively to signals falsely
identified as being caused by a transit exoplanet when it is actually a
systematic false alarm (noise) or an astrophysical false positive.
In the following paragraphs, we detail our method for addressing these
challenges and quantifying their effects.
In summary, we identify false alarms by developing a conservative automated
candidate vetting algorithm using the full light curve of each target star and
measure the incompleteness introduced by this procedure.
To account for astrophysical false positives, we discard candidates that fail
the standard transit centroid tests and then statistically incorporate
uncertainties introduced by false positives missed by this procedure at a
population level.
